\documentclass[9pt,letterpaper]{article}

%-----------------------------------------------------------
% PACKAGES & SETTINGS
%-----------------------------------------------------------
\usepackage[margin=0.3in]{geometry} % Narrower margins
\usepackage[default]{lato}          % Clean, compact sans-serif font
\usepackage{fontawesome5}           % Icons for GitHub, LinkedIn, Email, Phone
\usepackage{enumitem}               % Tighter bullet spacing
\usepackage{xcolor}                 % Color for headings
\usepackage{hyperref}               % Clickable links
\usepackage{parskip}                % No paragraph indentation

% Custom color
\definecolor{myblue}{RGB}{0, 102, 204} % Professional blue

% Optimized list spacing:
\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=0pt, parsep=0pt}
\setlength{\parskip}{0pt} % Minimal paragraph spacing

\pagestyle{empty}  % No page numbers

% Section headings with NO EXTRA SPACE ABOVE OR BELOW
\newcommand{\sectionHeading}[1]{%
  \noindent\textbf{\large\textcolor{myblue}{#1}}%
  \par\vspace{-1.5ex}%  <-- adjust this value
  \noindent\textcolor{myblue}{\rule{\linewidth}{0.7pt}}%
}

\begin{document}

%----------------- HEADER -----------------%
\begin{center}
  {\LARGE \textbf{Michael Meyers}}\\
  \vspace{0.5pt}
  Titusville, FL \quad 
  \href{mailto:mwmeyers03@gmail.com}{\textcolor{myblue}{\faEnvelope\; mwmeyers03@gmail.com}}\quad
  \faPhone\; 407-782-2620\quad
  \href{https://github.com/mwmeyers03}{\textcolor{myblue}{\faGithub\; mwmeyers03}}\quad
  \href{https://www.linkedin.com/in/michael-meyers-37b0071b1/}{\textcolor{myblue}{\faLinkedin\; LinkedIn}}
\end{center}

%\textcolor{myblue}{\rule{\linewidth}{0.7pt}}

%----------------- EDUCATION -----------------%
\sectionHeading{Education}
\textbf{University of Central Florida} 
\hfill \textit{Est. Graduation: Dec 2026}\\
\textit{M.S. in Electrical Engineering} \quad(\textbf{GPA:} 4.0)\\
\textbf{University of Central Florida} 
\hfill \textit{May 2025}\\
\textit{B.S. in Electrical Engineering, B.S. in Biomedical Sciences} \quad(\textbf{GPA:} 3.75)\\
Minor in Mathematical Biology, Honors in the Majors

%----------------- WORK EXPERIENCE -----------------%
\sectionHeading{Work Experience}

\textbf{Associate Electromechanical Engineer -- Northrop Grumman}
\hfill \textit{June 2025 -- Present}\\
Melbourne, FL
\begin{itemize}
  \item Design electrical diagrams for instrumentation setup on the TACAMO Program.
  \item Design and deliver cable‑assembly wiring diagrams and harness layouts in AutoCAD Electrical, ensuring strict compliance with MIL‑STD‑1553, MIL‑STD‑1760, and other relevant aerospace electromechanical standards.
  \item Manage the end‑to‑end review cycle in an Agile environment, conducting peer‑reviews and status updates that guarantee drawing accuracy and timely approvals across multidisciplinary teams.



 
\end{itemize}

\textbf{Associate Control Systems Engineer -- Mitsubishi Power Americas} 
\hfill \textit{Sep 2024 -- May 2025}\\
Lake Mary, FL
\begin{itemize}
  \item Designed and assessed gas turbine control systems, focusing on HMI and validating control logic.
  \item Developed scripts to streamline lengthy workflows through VBA automation, saving 300 hours annually and enhancing accuracy.
  \item Conducted thorough communication tests for digital and analog I/O to validate control system functionality.
  \item  Led the installation, setup and backup of essential control system machines, including network switches and servers.
\end{itemize}

\textbf{Integration \& Test Engineer Intern -- Northrop Grumman}
\hfill \textit{May 2023 -- Sep 2024}\\
Melbourne, FL
\begin{itemize}
  \item Established essential lab infrastructure to improve team accessibility and performance.
  \item Supported Lab Operations across all Integrated Platform Tests (IPTs) on the Strike Program's SEL.
  \item Created automation scripts in Python, PowerShell, and Groovy, saving ~500 hours annually.
  \item Aided overall lab operations and test support of real‐time systems and subsystems in over 5 labs.
\end{itemize}

\textbf{Undergraduate Research Assistant -- UCF NanoBioSensors Laboratory}
\hfill \textit{May 2022 -- Jan 2024}\\
Orlando, FL
\begin{itemize}
  \item Conducted research and development of a wireless bioimpedance sensor leveraging BLE technology, utilizing a 2-layer FlexPCB.
  \item Integrated a novel 3D‐printed microsensor with microcontrollers to enhance capabilities.
  \item Fabricated and characterized impedance measurements of sensing devices for accuracy.
\end{itemize}

\textbf{Manufacturing Engineer Intern -- MtronPTI}
\hfill \textit{Oct 2022 -- May 2023}\\
Orlando, FL
\begin{itemize}
  \item Built electrical and electronic systems, including a temperature‐regulated curing oven and an acid mixer.
  \item Analyzed component specifications and evaluated compliance with documented requirements.
  \item Tested and recorded product performance, including phase noise analysis and capacitor dicing.
  \item Documented processes and procedures for troubleshooting various oscillator fixtures.
\end{itemize}

%----------------- SKILLS -----------------%
\sectionHeading{Skills}
{\small
\begin{itemize}
  \item \textbf{Programming Languages:} Python | Java | C | C++ | PowerShell | Verilog | SQL | MATLAB | UML/SysML
  \item \textbf{Classes:} Electronics 2 | Image Processing | DSP Applications | Mathematical Biology | SAW Devices \& Systems | Computer Vision
  \item \textbf{Software:} AutoCAD Electrical
 % | IsoPro% 
  | SolidWorks | KiCAD/Altium | Jira | Confluence | Bitbucket | Bamboo | Cameo | Ansys EM | ADS
  \item \textbf{Certifications:} Biotechnician Assistant | Photoshop | Microsoft PowerPoint | Word | Excel
\end{itemize}
}

%----------------- PROJECTS -----------------%
\sectionHeading{Projects}

\textbf{Net Worth Projection App -- Personal Project}
\hfill \textit{Feb 2026 -- Present}
\begin{itemize}
  \item Engineered a financial simulation platform using Svelte, TypeScript, and Web Workers to model multi-decade retirement outcomes, portfolio growth, cash flow, and withdrawal sustainability for dual-income households.
  \item Developed a scenario-analysis engine (Conservative/Expected/Aggressive) with allocation-based return modeling, retirement trigger logic, failure-year detection, ending-balance retention metrics, and exportable reporting (CSV/JSON) for decision support.
  \item Built advanced parameter-management UX with state-driven controls (person-specific and combined views), reactive data stores, and high-performance computation offloading to deliver responsive retirement projections under varying market conditions.
\end{itemize}

\textbf{DIY Digital Audio Mixer -- University of Central Florida}
\hfill \textit{May 2024 -- May 2025}
\begin{itemize}
  \item Conducted research and development on analog audio circuitry to design a low-cost, high-performance audio mixer.
  \item Designed four separate compact 4-layer PCBs to accommodate the full mixed-signal chain while supporting phantom power capabilities (Power Supply PCB, STM32 MCU PCB, Analog Signal PCB, Digital Signal PCB).
  \item Programmed DSP algorithms on a Raspberry Pi 5 system to enable real-time, 8-channel audio processing.
  \item Achieved an overall SNR of 50, $<$10ms latency and supported 8-channel real-time control via webapp and functional AI automixing feature.
\end{itemize}



% \textbf{Garduino -- Robotics Club of Central Florida} 
% \hfill \textit{Feb 2022 -- Jul 2022}
% \begin{itemize}
%   \item Improved greenhouse designs in SolidWorks, optimizing the roofing system for efficient control.
%   \item Developed a C++ automation system to monitor moisture sensor data and automate greenhouse ventilation.
% \end{itemize}

% %----------------- CAMPUS INVOLVEMENT -----------------%
% \sectionHeading{Campus Involvement}

% \textbf{IEEE EMBS UCF -- Founder \& President}
% \hfill \textit{May 2024 -- May 2025}
% \begin{itemize}
%   \item Planned and organized all aspects of a new student branch, supporting over 100 members.
%   \item Secured \$4,000 in sponsorship funding for student-led projects (Oxygen Concentrator, Sole Pressure Sensor).
% \end{itemize}

% \textbf{IEEE UCF -- Secretary \& Outreach Chair}
% \hfill \textit{Nov 2022 -- May 2024}
% \begin{itemize}
%   \item Authored and managed the biweekly IEEE newsletter for 300+ students and obtained over \$10,000 in sponsorships.
% \end{itemize}

\end{document}
